---
title: "task3"
author: "Dovile Oganauskaite"
date: '2016 m rugsėjis 23 d '
output: html_document
---
##Feature of R

Introduction
Leaflet is one of the most popular open-source JavaScript libraries for interactive maps. It's used by websites ranging from The New York Times and The Washington Post to GitHub and Flickr, as well as GIS specialists like OpenStreetMap, Mapbox, and CartoDB.

This R package makes it easy to integrate and control Leaflet maps in R.

Features
Interactive panning/zooming
Compose maps using arbitrary combinations of:
Map tiles
Markers
Polygons
Lines
Popups
GeoJSON
Create maps right from the R console or RStudio
Embed maps in knitr/R Markdown documents and Shiny apps
Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns
Use map bounds and mouse events to drive Shiny logic
Installation
To install this R package, run this command at your R prompt:

```{r}
install.packages("leaflet")
# to install the development version from Github, run
# devtools::install_github("rstudio/leaflet")
```

Once installed, you can use this package at the R console, within R Markdown documents, and within Shiny applications.

Basic Usage
You create a Leaflet map with these basic steps:

Create a map widget by calling leaflet().
Add layers (i.e., features) to the map by using layer functions (e.g. addTiles, addMarkers, addPolygons) to modify the map widget.
Repeat step 2 as desired.
Print the map widget to display it.
Here's a basic example:
```{r}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m  # Print the map
```

In case you're not familiar with the magrittr pipe operator (%>%), here is the equivalent without using pipes:
```{r}
m <- leaflet()
m <- addTiles(m)
m <- addMarkers(m, lng=174.768, lat=-36.852, popup="The birthplace of R")
m
```

Next Steps
We highly recommend that you proceed to The Map Widget page before exploring the rest of this site, as it describes common idioms we'll use throughout the examples on the other pages.

Although we have tried to provide an R-like interface to Leaflet, you may want to check out the API documentation of Leaflet occasionally when the meanings of certain parameters are not clear to you.
